\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2015-08-02 paper.tex
Correction from eragmus
Fix a few minor typos

The payment network Visa has achieved 47,000 peak transactions per second on its
network during the 2013 holidays\cite{visa}, and averages hundreds of millions
per day. Currently, Bitcoin supports less than 7 transactions per second with a
1 megabyte block limit. If we use an average of 300 bytes per bitcoin
transaction and assumed unlimited block sizes, an equivalent capacity to peak
Visa transaction volume of 47,000/tps would be nearly 8 gigabytes per Bitcoin
block, every ten minutes on average. Continuously, that would be over 400
petabytes per year. Clearly, that isn't feasible today. No home computer in the
world can operate with that kind of bandwidth and storage. If Bitcoin is to
replace all electronic payments in the future, not just Visa, it would result in
outright collapse of the Bitcoin network, or at best, extreme centralization of
Bitcoin nodes and miners to the only ones who could afford it. This
centralization would then defeat aspects of network decentralization that make
Bitcoin secure, as the ability for entities to validate the chain is what
allows Bitcoin to ensure ledger accuracy and security. Having fewer validators
due to larger blocks not only implies fewer individuals ensuring ledger
accuracy, but also results in fewer entities that would be able to validate the
blockchain as part of the mining process, which results in encouraging miner
centralization. Extremely large blocks, for example in the above case of 8
gigabytes every 10 minutes on average, would imply that only a few parties
would be able to do block validation. This creates a great possibility that
entities will end up trusting centralized parties. Having privileged trusted
parties creates a social trap whereby the central party will not act in the
interest of an individual (principal-agent problem), e.g. rentierism by
charging higher fees to mitigate the incentive to act dishonestly. In extreme
cases, this manifests as individuals sending funds to centralized trusted
custodians who have full custody of customers funds. Such arrangements, as are
common today, create severe counterparty risk. A prerequisite to prevent that
kind of centralization from occurring would require the ability for bitcoin to
be validated by a single consumer-level computer on a home broadband
connection. By ensuring that full validation can occur cheaply, Bitcoin nodes
and miners will be able to prevent extreme centralization and trust, which
ensures extremely low transaction fees.

@@

The intent of creating a new Commitment Transaction is to invalidate all old
Commitment Transactions when updating the new balance with a new Commitment
Transaction. Invalidation of old transactions can happen by making an output be
a Revocable Sequence Verification Contract (RSMC). To invalidate a transaction,
a superseding transaction will be signed and exchanged by both parties that 
gives all funds to the counterparty in the event an older transaction is
incorrectly broadcast. The incorrect broadcast is identified by creating two
different Commitment Transactions with the same final balance outputs, however
the payment to oneself is encumbered by a RSMC.

@@

After the Commitment Transaction has been in the blockchain for 1000 blocks,
Bob can then broadcast the Revocable Delivery transaction. He must wait 1000
blocks to prove he has not revoked this Commitment Transaction (C1b). After
1000 blocks, the Revoable Delivery transaction will be able to be included in a
block. If it is attempted to be included in a block before 1000 confirmations,
the transaction will be invalid up until after 1000 confirmations have passed
(at which point it will become valid if the output has not yet been redeemed).

@@

Due to this fact, one will likely delete all prior Commitment Transactions when
a Breach Remedy Transaction has been passed to the counterparty. If one
broadcasts an incorrect (deprecated and invalidated Commitment Transaction), all
the money will go to one's counterparty. For example, if Bob broadcasts C1b, so
long as Alice watches the blockchain within the predefined number of blocks (in
this case, 1000 blocks), Alice will be able to take all the money in this
channel by broadcasting RD1b. Even if the present balance of the Commitment
state (C2a/C2b) is 0.4 BTC to Alice and 0.6 BTC to Bob, because Bob violated the
terms of the contract, all the money goes to Alice as a penalty. Functionally,
the Revocable Transaction acts as a proof to the blockchain that Bob has
violated the terms in the channel and this is programatically adjudicated by the
blockchain.

>>>>

The payment network Visa has achieved 47,000 peak transactions per second on its
network during the 2013 holidays\cite{visa}, and averages hundreds of millions
per day. Currently, Bitcoin supports less than 7 transactions per second with a
1 megabyte block limit. If we use an average of 300 bytes per bitcoin
transaction and assumed unlimited block sizes, an equivalent capacity to peak
Visa transaction volume of 47,000/tps would be nearly 8 gigabytes per Bitcoin
block, every ten minutes on average. Continuously, that would be over 400
terabytes per year. Clearly, that isn't feasible today. No home computer in the
world can operate with that kind of bandwidth and storage. If Bitcoin is to
replace all electronic payments in the future, not just Visa, it would result in
outright collapse of the Bitcoin network, or at best, extreme centralization of
Bitcoin nodes and miners to the only ones who could afford it. This
centralization would then defeat aspects of network decentralization that make
Bitcoin secure, as the ability for entities to validate the chain is what
allows Bitcoin to ensure ledger accuracy and security. Having fewer validators
due to larger blocks not only implies fewer individuals ensuring ledger
accuracy, but also results in fewer entities that would be able to validate the
blockchain as part of the mining process, which results in encouraging miner
centralization. Extremely large blocks, for example in the above case of 8
gigabytes every 10 minutes on average, would imply that only a few parties
would be able to do block validation. This creates a great possibility that
entities will end up trusting centralized parties. Having privileged trusted
parties creates a social trap whereby the central party will not act in the
interest of an individual (principal-agent problem), e.g. rentierism by
charging higher fees to mitigate the incentive to act dishonestly. In extreme
cases, this manifests as individuals sending funds to centralized trusted
custodians who have full custody of customers funds. Such arrangements, as are
common today, create severe counterparty risk. A prerequisite to prevent that
kind of centralization from occurring would require the ability for bitcoin to
be validated by a single consumer-level computer on a home broadband
connection. By ensuring that full validation can occur cheaply, Bitcoin nodes
and miners will be able to prevent extreme centralization and trust, which
ensures extremely low transaction fees.

@@

The intent of creating a new Commitment Transaction is to invalidate all old
Commitment Transactions when updating the new balance with a new Commitment
Transaction. Invalidation of old transactions can happen by making an output be
a Revocable Sequence Maturity Contract (RSMC). To invalidate a transaction,
a superseding transaction will be signed and exchanged by both parties that 
gives all funds to the counterparty in the event an older transaction is
incorrectly broadcast. The incorrect broadcast is identified by creating two
different Commitment Transactions with the same final balance outputs, however
the payment to oneself is encumbered by a RSMC.

@@

After the Commitment Transaction has been in the blockchain for 1000 blocks,
Bob can then broadcast the Revocable Delivery transaction. He must wait 1000
blocks to prove he has not revoked this Commitment Transaction (C1b). After
1000 blocks, the Revocable Delivery transaction will be able to be included in a
block. If it is attempted to be included in a block before 1000 confirmations,
the transaction will be invalid up until after 1000 confirmations have passed
(at which point it will become valid if the output has not yet been redeemed).

@@

Due to this fact, one will likely delete all prior Commitment Transactions when
a Breach Remedy Transaction has been passed to the counterparty. If one
broadcasts an incorrect (deprecated and invalidated Commitment Transaction), all
the money will go to one's counterparty. For example, if Bob broadcasts C1b, so
long as Alice watches the blockchain within the predefined number of blocks (in
this case, 1000 blocks), Alice will be able to take all the money in this
channel by broadcasting BR1b. Even if the present balance of the Commitment
state (C2a/C2b) is 0.4 BTC to Alice and 0.6 BTC to Bob, because Bob violated the
terms of the contract, all the money goes to Alice as a penalty. Functionally,
the Revocable Transaction acts as a proof to the blockchain that Bob has
violated the terms in the channel and this is programatically adjudicated by the
blockchain.
